\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-11-06 src/chain.tex
dp
FPT + FT

@@

\subsection{Fault Tolerance on Layered Graph}
We first assume that the input graph is a directed layered graph, i.e.
$G = (\bigcup_{i = 1}^l L_i, A)$ where 
$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
placement does not exist.
The algorithm uses dynamic programming.
We find the optimal 2-robust placement for every  
combination of two physical vertices from the same layer, 
and every combination of two virtual functions.
Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
One can verified that the following recursive formula holds:
$$
ft(v_1, v_2, \alpha_1, \alpha_2) = 
\min_{
\begin{subarray}{c}
u_1,u_2,(\beta_1,\beta_2:
\\
u_1
\\
asdf
\end{subarray}
}
$$

\subsection{Layered Graph Transformation}
Given a directed acyclic graph $G = (V, A)$, 
and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
We set the processing capacity of each internal vertex on this path to be zero,
and the bandwidth of the arcs along the path to be $b(u,v)$.
It is easy to see that the resulting graph is indeed a layered graph and that every placement
on $G$ corresponds to a placement on $G'$ with the same cost.
Figure~\ref{fig:layer-transform} depicts this process.
\begin{figure}
\caption{
\label{fig:layer-transform}
}
\begin{center}
\input{layer-transform}
\end{center}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{FPT Algorithm for General Networks}
We now propose an FPT algorithm for general networks that is similar to the randomized 
algorithm from Section~\ref{sec:general}.
Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
vertices in the graph, $A$ is the time required to find a solution on a DAG,
and $O$ is the time required to orient the graph given a permutation on the neighborly
vertices, as discussed above.
The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
once for any orientation results from any of the $k!$ possible permutations and
returns the best solution.
The following theorem follows immediately.

\begin{theorem}
There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after $k!$ iterations 
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Fault Tolerance on Layered Graph}
We first assume that the input graph is a directed layered graph, i.e.
$G = (\bigcup_{i = 1}^l L_i, A)$ where 
$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
placement does not exist.
The algorithm uses dynamic programming.
We find the optimal 2-robust placement for every  
combination of two physical vertices from the same layer, 
and every combination of two virtual functions.
Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
One can verified that the following recursive formula holds:
$$
ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
\begin{cases}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
\end{cases}
$$

where
$$
\begin{array}{l}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1 \in \calE:
	\\
	\beta'_1 \prec \gamma_1 
	}}}
ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
\end{array}
$$

\begin{theorem}
There is an algorithm that, on a layered graph, finds an optimal 2-robust placement in 
polynomial time. 
\end{theorem}

\begin{proof}
One can verify, that using dynamic programming, the above recursive can be solved in polynomial time,
using backtracking we can also find the optimal solution.
\end{proof}

We note that the above algorithm does not take into account the latency constraint.
It is possible, however, given a latency constraint, $L$, to modify the algorithm to return
an optimal solution such that the total latency of the two placements is no more than $2L$.
Such a solution is guaranteed to be optimal in terms of costs.
It is also easy to see that in such solution at least one of the placements has lower latency 
than $L$ and the other one has latency that is at most $2L$.

\subsection{Layered Graph Transformation}
Given a directed acyclic graph $G = (V, A)$, 
and let $\pi:V \to [n]$ be an arbitrary topological sorting of $G$ 
we transform it into a layered graph $G'$ by replacing every edge $(u, v)$ with a directed path of 
length (number of arcs) $\pi(v) - \pi(u)$ from $u$ to $v$.
We set the processing capacity of each internal vertex on this path to be zero,
and the bandwidth of the arcs along the path to be $b(u,v)$.
It is easy to see that the resulting graph is indeed a layered graph and that every placement
on $G$ corresponds to a placement on $G'$ with the same cost.
Figure~\ref{fig:layer-transform} depicts this process.
\begin{figure}
\captionsetup{singlelinecheck=off}
\caption[layered]{foo
\label{fig:layer-transform}
\begin{enumerate}
\item A directed acyclic graph that is not a layered graph
  \item A topological sorting of the above graph
  \item A layered graph obtained by replacing crossing arcs with simple paths 
\end{enumerate}}
\begin{center}
\input{layer-transform}
\end{center}
\end{figure}
